---
title: "Regression Project"
output: html_document
---

#Executive Summary

Overall my analysis tells me the transmission type doesn't really have a significant impact on the fuel economy of a car once you account for other factors, such as weight and number of cyllinders.







#Results

```{r}
mtcars$am <- factor(mtcars$am, levels=c(0, 1), labels=c('Auto', 'Man'))
mtcars$vs <- factor(mtcars$vs, levels=c(0, 1), labels=c('V', 'S'))
lm1 <- lm(mpg ~ am + wt, mtcars)
summary(lm1)
lm2 <- lm(mpg ~ vs + wt + cyl, mtcars)
summary(lm2)
```

The model above shows that weight has a clear negative effect on the miles per gallon. There is a drop of 5.35 miles per gallon for every additional 1000 pounds of weight. However no significant changed is incurred due to the type of transmission.

In the second model, the transmission type doesn't have much impact once you account for weight and number of cyllinders, as the coefficients suggest.

```{r}
library(car)
scatterplot(mpg ~ wt | am, data=mtcars, 
  	xlab="Weight", ylab="Miles Per Gallon", 
   main="Scatter Plot", 
   labels=row.names(mtcars))
```

